
```{r setup, echo=FALSE, eval=TRUE}
knitr::opts_chunk$set(
  message = FALSE, warnings = FALSE,
  fig.height = 8, fig.width = 10, dev = "png"
)
```

```{r get-params, echo=FALSE}
cell_line <- params$cell_line
target <- params$target
treat_levels <- params$treat_levels
```

## Introduction

This is a workflow designed to directly compare the output of multiple approaches to detection of Differential (ChIP) Signal, specifically with regard to those available in the `extraChIPs` package.
Analysis using `DiffBind` will also be included as a reference standard, especially when using methods which should replicate this methodology.

The methods being compared will be

| Abbreviation  | Package | Windows | Normalisation | Method |
|:------------- |:-------- |:------- |:------------- |:------ |
| DB: LS        | DiffBind | Fixed   | Library Size  | QLF    |
| DB: TMM       | DiffBind | Fixed   | TMM           | QLF    |
| EC: LS        | extraChIPS | Fixed   | Library Size  | QLF    |
| EC: TMM       | extraChIPS | Fixed   | TMM           | QLF    |
| EC: TMMG      | extraChIPS | Fixed   | TMM Groups    | QLF    |
| EC: SQN       | extraChIPS | Fixed   | qsmooth       | QLF    |
| EC: SQNGC     | extraChIPS | Fixed   | qsmoothGC     | QLF    |
| EC: CQN       | extraChIPS | Fixed   | CQN           | QLF    |
