---
title: "Home"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---

```{r setup, echo=FALSE, eval=TRUE}
knitr::opts_chunk$set(
  message = FALSE, warning = FALSE,
  fig.height = 8, fig.width = 10, dev = "png", fig.align = "center"
)
```

```{r packages}
library(tidyverse)
library(reactable)
library(htmltools)
```


```{r, echo = FALSE, eval = TRUE, results='asis'}
cat(readLines(here::here("README.md")), sep = "\n")
```


## Analysis

Each method was given a score for each dataset, representing (-1) Not Recommended, (0) Viable But Lacking in some characteristic such as statistical power, and (1) for Recommended.
Any suggestion of spurious detections, or an introduced bias were assigned -1.
Scores were then totalled across datasets to provide guidance for methods which were robust overall and are generally applicable.
Scores were also totalled within datasets to provide guidance as to the sensitivity of each dataset to the chosen methods, with high scores representing a dataset with few technical challenges.

It was noted that there were notable differences in the sites identified under the sliding and fixed-width approaches.
Sites omitted from sliding-window analyses generally appeared be at the low end of signal, whilst this was less evident for sites exclusive to siding-window approaches.
Despite their apparent lack of power in some circumstances, this shift away from sites at the low end of signal was considered advantageous in reality and these methods were scored with that in mind.



```{r set-methods}
methods <- c(
  "DB-LS", "DB-TMM", 
  paste("FW", c("LS", "TMM", "TMMG", "CQN", "CQNG", "SQN", "SQNGC", "LT"), sep = "-"),
  paste("SW", c("LS", "TMM", "TMMG", "CQN", "CQNG", "SQN", "SQNGC", "LT", "LTSQN", "LTSQNGC"), sep = "-")
)
scores <- tibble(
  method = methods,
  `PRJNA509779 (AR)` = case_when(
    method %in% c(
      paste("DB", "TMM", sep = "-"), 
      paste("FW", c("CQN", "TMM", "SQN", "SQNGC"), sep = "-"),
      paste("SW", c("CQN", "TMM", "SQN", "LTSQNGC"), sep = "-")
    ) ~ -1,
    method %in% c(
      paste("DB", "LS", sep = "-"), 
      paste("FW", c("LS", "LT", "TMMG", "CQNG"), sep = "-"),
      paste("SW", c("CQNG", "TMMG", "LTSQN", "SQNGC", "LT", "LS"), sep = "-")
    ) ~ 1,
    TRUE ~ 0
  ),
  `PRJNA509779 (ER)` = case_when(
    method %in% c(
      paste("DB", c(), sep = "-"),
      paste("FW", c("CQN", "CQNG"), sep = "-"),
      paste("SW", c("CQN", "CQNG", "LTSQNGC"), sep = "-")
    ) ~ -1,
    method %in% c(
      paste("DB", c("TMM"), sep = "-"), 
      paste("FW", c("SQN", "TMM"), sep = "-"),
      paste("SW", c("LTSQN", "SQN", "SQNGC", "TMM"), sep = "-")
    ) ~ 1,
    TRUE ~ 0
  ),
  `PRJNA509779 (H3K27ac)` = case_when(
    method %in% c(
      paste("DB", c(), sep = "-"),
      paste("FW", c("CQNG"), sep = "-"),
      paste("SW", c("SQN", "SQNGC", "LTCQNGC"), sep = "-")
    ) ~ -1,
    method %in% c(
      paste("DB", c("LS", "TMM"), sep = "-"), 
      paste("FW", c("LS", "TMM", "TMMG", "CQN", "SQN", "LT"), sep = "-"),
      paste("SW", c("TMMG", "CQNG", "LTSQN", "CQN", "TMM", "LS", "LT"), sep = "-")
    ) ~ 1,
    TRUE ~ 0
  ),
  `MDA-MB-453 (AR)` = case_when(
    method %in% c(
      paste("DB", c("TMM"), sep = "-"), 
      paste("FW", c("SQN", "SQNGC", "TMM", "CQN"), sep = "-"),
      paste("SW", c("CQN", "TMM"), sep = "-")
    ) ~ -1,
    method %in% c(
      paste("DB", c("LS"), sep = "-"), 
      paste("FW", c("CQNG", "TMMG", "LS", "LT"), sep = "-"),
      paste("SW", c("CQNG", "TMMG", "LTSQN", "SQN", "SQNGC", "LTSQNGC", "LS", "LT"), sep = "-")
    ) ~ 1,
    TRUE ~ 0
  ),
  `MDA-MB-453 (GATA3)` = case_when(
    method %in% c(
      paste("DB", c("TMM"), sep = "-"), 
      paste("FW", c("TMM", "CQN", "SQNGC", "SQN"), sep = "-"),
      paste("SW", c("CQN", "TMM", "LTSQNGC"), sep = "-")
    ) ~ -1,
    method %in% c(
      paste("DB", c("LS"), sep = "-"), 
      paste("FW", c("LS", "LT", "TMMG", "CQNG"), sep = "-"),
      paste("SW", c("LS", "TMMG", "CQNG", "LT"), sep = "-")
    ) ~ 1,
    TRUE ~ 0
  ),
  `MDA-MB-453 (H3K27ac)` = case_when(
    method %in% c(
      paste("DB", c(), sep = "-"), 
      paste("FW", c(), sep = "-"),
      paste("SW", c("CQN", "LTSQNGC"), sep = "-")
    ) ~ -1,
    method %in% c(
      paste("DB", c("LS", "TMM"), sep = "-"), 
      paste("FW", c("LS", "TMM", "TMMG", "CQN", "CQNG", "SQN", "SQNGC", "LT"), sep = "-"),
      paste("SW", c("LS", "TMM", "TMMG", "CQNGC", "LT", "LTSQN"), sep = "-")
    ) ~ 1,
    TRUE ~ 0
  )
) %>% 
  mutate(
    score = dplyr::select(., -all_of("method")) %>% 
      as.matrix() %>% 
      rowSums(),
    package = ifelse(grepl("^DB", method), "DiffBind", "extraChIPs"),
    model = ifelse(grepl("LT", method), "limma-trend", "glmQLF"),
    windows = ifelse(grepl("^SW", method), "Sliding", "Fixed-Width"),
    groups = ifelse(grepl("(SQ|G$)", method), "Explicit", "None"),
    normalisation = str_remove_all(method, ".+-") %>% 
      str_remove_all("(^LT|G$)") %>% 
      str_replace_all("SQNGC", "SQN-GC") %>% 
      str_replace_all("^$", "LS")
  )
```

```{r tbl-summary}
tbl <- scores %>% 
  arrange(desc(score)) %>% 
  dplyr::select(
    method, windows, package, model, normalisation, groups, score, everything()
  ) %>% 
  reactable(
    sortable = TRUE, filterable = TRUE, pagination = FALSE,
    columns = list(
      method = colDef(
        name = "Method", footer = htmltools::tags$b("All Methods"), 
        maxWidth = 150
      ),
      package = colDef(name = "Package", footer = "", maxWidth = 110),
      model = colDef(name = "Model", footer = "", maxWidth = 110),
      score = colDef(name = "Score", footer = "", maxWidth = 60),
      groups = colDef(name = "Groups", footer = "", maxWidth = 110),
      windows = colDef(name = "Windows", footer = "", maxWidth = 110),
      normalisation = colDef(name = "Norm.", footer = ""),
      "PRJNA509779 (AR)" = colDef(name = "AR", maxWidth = 60, show = FALSE),
      "PRJNA509779 (ER)" = colDef(name = "ER", maxWidth = 60, show = FALSE),
      "PRJNA509779 (H3K27ac)" = colDef(name = "H3K27ac", show = FALSE),
      "MDA-MB-453 (AR)" = colDef(name = "AR", maxWidth = 60, show = FALSE),
      "MDA-MB-453 (GATA3)" = colDef(name = "AR", maxWidth = 60, show = FALSE),
      "MDA-MB-453 (H3K27ac)" = colDef(name = "AR", maxWidth = 60, show = FALSE)
    ),
    # columnGroups = list(
    #   colGroup(name = "PRJNA509779", columns = str_subset(names(.), "PRJNA509779"))
    # ),
    defaultColDef = colDef(
      maxWidth = 100, 
      style = function(value) {
        clr <- "black"
        if (value < 0) clr <- "red"
        list(color = clr, fontize = 10)
      },
      footer = function(values) htmltools::tags$b(sum(values))
    )
  )
cp <- htmltools::tags$caption(
  htmltools::em(
    "
    Summary of all tested methods across all datasets. Methods were scored 
    based on the methods described above and the combined score represents a
    measure of how difficult each method is to use. Highly-scoring methods 
    appear more robust across a diversity of settings. It should be noted,
    however, that in the  case of methods such as TMM, performing a simple
    test a priori for the suitability of using groups in the normalisation, 
    would restore these mthods much higher on the list
    "
  )
)
div(
  class = "table",
  div(class = "table-header", cp),
  tbl
)
```

```{r score-heatmap, fig.cap = "Heatmap of scores from individual datasets. Green indicates a recommended approach, whilst red indicates a highly problematic approach"}
scores %>% 
  arrange(desc(score)) %>% 
  dplyr::select(method, contains("(")) %>% 
  as.data.frame() %>% 
  column_to_rownames("method") %>% 
  pheatmap::pheatmap(
    color = c("red", "white", "forestgreen"), 
    cutree_rows = 4,
    legend_breaks = seq(-1, 1, by = 1), legend_labels = c(-1, 0, 1)
  )
```

## Conclusion

Some methods clearly stood as being applicable:

- Limma-Trend using logCPM values was appropriate for:
  - Fixed Windows
  - Sliding Windows (logCPM or SQ-Normalised)
  
- QLF Models were appropriate
  - Library Size Normalisation (Fixed or Sliding Windows)
  - TMM Normalisation **after testing** for group differences (Fixed or Sliding)
  
Datasets failing a permutation test using `quantro` using raw counts were AR (both datasets) and GATA3.
Incorporating a quantro test when using TMM will enable this to be applied widely.
Interestingly, most datasets failed this test when using logCPM values, perhaps suggesting this test is too sensitive for this data type, or is even misleading

In addition, H3K27ac appeared to perform more poorly using sliding windows.
However, the majority of sites 'lost' were low signal sites, with a number of new sites detected in the middle of the signal range.
Choosing the optimal method may require careful consideration.

Thus the final options for GRAVI should be

1. Fixed-Width: QLF-none, QLF-TMM(+G), LT-none
2. Sliding Windows: QLF-none, QLF-TMM(+G), LT-none, LT-SQN

Previous work has also suggested the *limma-trend* methods lose comparatively more power when applying *treat* and this requires testing.
A final comparison of these 7 methods, along with the impact of *treat* is required next.
